### 2024-02-09 paper_sisc_first_revision/localpsf.tex
editing figures with noemi

\section{Overview of the method and illustration on a blur operator}

Before delving into technical details, we provide an overview of the method. Along the way, we illustrate steps using a spatially variant blur example, in which the integral kernel is given as follows:
$$\Phi(y,x) = (1 - a f(y,x)) g(x) \exp \left(-\frac{1}{2}h^T(y,x) C^{-1} h(y,x)\right).$$ 
Here, $h(y,x) = R(\theta(x)) (y-x)$, $R(\theta(x))$ is the 2D rotation matrix by angle $\theta(x) = (x^1 + x^2) \pi / 2$, $C = L^2 \operatorname{diag}(c_1, c_2)$, $g(x) = x^1(1-x^1)x^2(1-x^2)$,  and $f(x,y) = \cos\left(p^1(y,x) / \sqrt{c_1 / 2.0}\right) \sin\left(p^2(y,x) / \sqrt{c_2 / 2.0}\right)$ for some constants $a, L, c_1, c_2$. In this section we use $a=1.0$, $L^2=1.0$, $c_1=0.01$, and $c_2=0.0025$. Using this kernel, the impulse response $\phi_x$ is a bumpy blob that is centered near $x$, and is rotated and scaled in a manner that depends on $x$ (see Figure \ref{fig:frog1}). Note that for this operator, using our method is unnecessary because entries of the kernel are given directly via a formula. The purpose of this example is to illustrate the method using an operator which is known exactly and may be easily visualized.

%The constant $L$ controls how wide the blob is, and $a$ controls the bumpiness. With $a=0$, $\phi_x$ is a Gaussian. As $a$ increases, $\phi_x$ becomes more bumpy. When $a > 1$, the integral kernel contains negative values, which violates the assumptions of our method. In the numerical results section we will vary $a$ and $L$, even allowing $a>1$ to test the robustness of the method to violations of the non-negative kernel assumption.

\begin{figure}
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[scale=0.25]{kernel_impulse_illustration2.pdf}
%		\caption{Kernel and impulse responses}
		\label{fig:kernel_impulse_illustration}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
		\centering
		\includegraphics[scale=0.5]{frog_ellipsoid_width2.pdf}
%		\caption{Impulse response support ellipsoid}
		\label{fig:frog_ellipsoid_width}
	\end{subfigure}

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.25]{frog_moments2.pdf}	
	\caption{asdf3
	}
	\label{fig:frog2}
\end{figure}

@@

\section{Technical preliminaries}

@@

\subsection{Example 1: Inversion for the basal friction coefficient in an ice sheet flow problem}
\label{sec:ice}

@@

\subsection{Example 2: Inversion for the initial condition in an advective-diffusive transport problem}
\label{sec:adv}

>>>>

\begin{figure}
	\begin{center}
	\begin{subfigure}[b]{0.58\textwidth}
		\centering
		\includegraphics[scale=0.275]{kernel_impulse_illustration2.pdf}
%		\caption{Kernel and impulse responses}
		\label{fig:kernel_impulse_illustration}
	\end{subfigure}
	\begin{subfigure}[b]{0.41\textwidth}
		\centering
		\includegraphics[scale=0.55]{frog_ellipsoid_width2.pdf}
%		\caption{Impulse response support ellipsoid}
		\label{fig:frog_ellipsoid_width}
	\end{subfigure}
	\end{center}

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.28]{frog_moments2.pdf}	
	\caption{asdf3
	}
	\label{fig:frog2}
\end{figure}

@@

\section{Preliminaries}

@@

\subsection{Example 1: Spatially variant blur}

Before delving into technical details, we provide an overview of the method. Along the way, we illustrate steps using a spatially variant blur example, in which the integral kernel is given as follows:
$$\Phi(y,x) = (1 - a f(y,x)) g(x) \exp \left(-\frac{1}{2}h^T(y,x) C^{-1} h(y,x)\right).$$ 
Here, $h(y,x) = R(\theta(x)) (y-x)$, $R(\theta(x))$ is the 2D rotation matrix by angle $\theta(x) = (x^1 + x^2) \pi / 2$, $C = L^2 \operatorname{diag}(c_1, c_2)$, $g(x) = x^1(1-x^1)x^2(1-x^2)$,  and $f(x,y) = \cos\left(p^1(y,x) / \sqrt{c_1 / 2.0}\right) \sin\left(p^2(y,x) / \sqrt{c_2 / 2.0}\right)$ for some constants $a, L, c_1, c_2$. In this section we use $a=1.0$, $L^2=1.0$, $c_1=0.01$, and $c_2=0.0025$. Using this kernel, the impulse response $\phi_x$ is a bumpy blob that is centered near $x$, and is rotated and scaled in a manner that depends on $x$ (see Figure \ref{fig:frog1}). The constant $L$ controls how wide the blob is, and $a$ controls the bumpiness. With $a=0$, $\phi_x$ is a Gaussian. As $a$ increases, $\phi_x$ becomes more bumpy. When $a > 1$, the integral kernel contains negative values, which violates the assumptions of our method. Note that for this operator, using our method is unnecessary because entries of the kernel are given directly via a formula. The purpose of this example is to illustrate the method using an operator which is known exactly and may be easily visualized.

\subsection{Example 2: Inversion for the basal friction coefficient in an ice sheet flow problem}
\label{sec:ice}

@@

\subsection{Example 3: Inversion for the initial condition in an advective-diffusive transport problem}
\label{sec:adv}
